---
output: 
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  out.width = "100%"
)
```
## FastrCAT

Oceanographic data generated from SeaBird FastCAT CTD’s have been collected since 1995 under EcoFOCI. The file type which we can view and collate the data from is a SeaBird proprietary file type called an .up file. The .up file is a post process file generated from the SeaSoft software and only includes the data from the upward cast of the device. Since 1997 there have been various versions of a Perl script which will append important station header information to the .up file. The Perl script acts as an interface between the SeaSoft software and the MasterCOD .db3 file to extract the header information based on the BON/CALVET/TUCK number. Each station from a cruise has its’ own .up file. This format isn’t in a traditional tabular format and is not easily accessed by users. It has been determined that it would be useful to build an R package for the FastCAT data that starts with a function to aggregate each cruises .up files into a tabular format. The function can then be used to generate tabular data and as a QAQC process for the .up files. Then the tabular data be easily used to create plots and calculate indices.  This R package would be a final step in processing .up files while out at sea. The steps would be: enter COD form data into MasterCOD, run Perl script and then the R functions from the command line. 

## documentation

Full documentation of the process is available in vignettes

## install the package

There are two options for installing the package.

1. download/clone the project from GitLab and then install to R from source
2. install with the `devtools` package

### install via `devtools`

You'll need to setup ssh on GitLab and add your ssh key. Once that's done, 
the following R code should install the package

```{r, eval = FALSE}
library(devtools)

creds = git2r::cred_ssh_key("C:\\Users\\MYSELF\\.ssh\\id_rsa.pub",
                            "C:\\Users\\MYSELF\\.ssh\\id_rsa")
devtools::install_git("git@gitlab.afsc.noaa.gov:Nissa.Ferm/FastrCAT.git",
                      credentials = creds)
```

