---
title: "FastrCAT"
author: "Nissa Ferm"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

Oceanographic data generated from SeaBird FastCAT CTD’s have been collected since 1995 under EcoFOCI. The file type which we can view and collate the data from is a SeaBird proprietary file type called an .up file. The .up file is a post process file generated from the SeaSoft software and only includes the data from the upward cast of the device. Since 1997 there have been various versions of a Perl script which will append important station header information to the .up file. The Perl script acts as an interface between the SeaSoft software and the MasterCOD .db3 file to extract the header information based on the BON/CALVET/TUCK number. Each station from a cruise has its’ own .up file. This format isn’t in a traditional tabular format and is not easily accessed by users. It has been determined that it would be useful to build an R package for the FastCAT data that starts with a function to aggregate each cruises .up files into a tabular format. The function can then be used to generate tabular data and as a QAQC process for the .up files. Then the tabular data be easily used to create plots and calculate indices.  This R package would be a final step in processing .up files while out at sea. The steps would be: enter COD form data into MasterCOD, run Perl script and then the R functions from the command line. 




Vignettes are long form documentation commonly included in packages. Because they are part of the distribution of the package, they need to be as compact as possible. The `html_vignette` output type provides a custom style sheet (and tweaks some options) to ensure that the resulting html is as small as possible. The `html_vignette` format:

- Never uses retina figures
- Has a smaller default figure size
- Uses a custom CSS stylesheet instead of the default Twitter Bootstrap style

## Vignette Info

Note the various macros within the `vignette` section of the metadata block above. These are required in order to instruct R how to build the vignette. Note that you should change the `title` field and the `\VignetteIndexEntry` to match the title of your vignette.

## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```


